---
title: "Research Question"
format: html
editor: visual
---

## Research Question

### 1. What is the relationship between self-rated multiplication proficiency and actual multiplication fluency?

```{r}

cor.test(dataset$Multiplication_Fluency, dataset$Self_Rated_Proficiency)

```

### 2. How do sociodemographic factors (ethnicity, parental education, school type) influence multiplication fluency?

```{r}

lm1 <- lm(Multiplication_Fluency ~ Self_Rated_Proficiency + Ethnicity + Parental_Education + Math_Language + Language_Used + School_Type + Difficulties, data = dataset)
summary(lm1)

```

### 3. Do sociodemographic factors influence self-rated multiplication proficiency?

```{r}

# Multiplication Fluency as the dependent variable
model1 <- lmer(Multiplication_Fluency ~ Self_Rated_Proficiency + Ethnicity + Parental_Education + Math_Language + 
               Language_Used + School_Type + Difficulties + (1 | School_ID), data = dataset)
summary(model1)

# Self-Rated Proficiency as the dependent variable
model2 <- lmer(Self_Rated_Proficiency ~ Ethnicity + Parental_Education + Math_Language + 
               Language_Used + School_Type + Difficulties + (1 | School_ID), data = dataset)
summary(model2)

```

### 4. Is there a discrepancy between self-rated proficiency and actual fluency, and what factors contribute to this discrepancy?

```{r}

dataset$Discrepancy <- dataset$Self_Rated_Proficiency - dataset$Multiplication_Fluency
lm_discrepancy <- lm(Discrepancy ~ Ethnicity + Parental_Education + Math_Language + Language_Used + School_Type + Difficulties, data = dataset)
summary(lm_discrepancy)

```

### 5. How does the language used to learn multiplication and math language in primary school affect multiplication fluency and self-rated proficiency?

```{r}

# T-test for difficulties in learning multiplication
t.test(Multiplication_Fluency ~ Difficulties, data = dataset)
t.test(Self_Rated_Proficiency ~ Difficulties, data = dataset)

# ANOVA for other categorical variables
anova1 <- aov(Multiplication_Fluency ~ Ethnicity + Parental_Education + School_Type, data = dataset)
summary(anova1)

anova2 <- aov(Self_Rated_Proficiency ~ Ethnicity + Parental_Education + School_Type, data = dataset)
summary(anova2)

```

### 6. Do students with difficulties in learning multiplication have lower multiplication fluency and self-rated proficiency?

## Language-related analysis

### 1. Is there a relationship between the native language and the language used for learning math and multiplication in schools?

```{r}

# Crosstabulation
table_native_math <- table(dataset$Native_Language, dataset$Math_Language)
table_native_mult <- table(dataset$Native_Language, dataset$Language_Used)

# Chi-Square Test
chisq.test(table_native_math)
chisq.test(table_native_mult)
```

### 2. How does proficiency in second languages impact multiplication fluency and self-rated proficiency?

```{r}

# Assuming proficiency scores for second languages are stored in separate columns
lm2 <- lm(Multiplication_Fluency ~ Proficiency_Mandarin + Proficiency_English + Proficiency_Hokkien + 
          Proficiency_Cantonese + Proficiency_Malay + Ethnicity + Parental_Education + 
          Math_Language + Language_Used + School_Type + Difficulties, data = dataset)
summary(lm2)

lm3 <- lm(Self_Rated_Proficiency ~ Proficiency_Mandarin + Proficiency_English + Proficiency_Hokkien + 
          Proficiency_Cantonese + Proficiency_Malay + Ethnicity + Parental_Education + 
          Math_Language + Language_Used + School_Type + Difficulties, data = dataset)
summary(lm3)

```

### 3. Do students whose native language matches the language used for learning math and multiplication in schools perform better in multiplication fluency and self-rated proficiency?

### 4. Is there a difference in multiplication fluency and self-rated proficiency based on the number of languages spoken?

### 5. How does self-rated proficiency in second languages correlate with self-rated multiplication proficiency?
